---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# gggradient

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/gggradient)](https://CRAN.R-project.org/package=gggradient)
<!-- badges: end -->

The goal of gggradient is to provide a flexible ggplot2 interface with
`grid::linearGradient()` using familiar fill scale syntax.

## Installation

You can install the development version of gggradient from GitHub like so:

``` r
# install.packages("pak")
pak::pak("hrryt/gggradient")
```

## Examples

Easily create a gradient fill along a geometry:

```{r}
library(ggplot2)
library(gggradient)

ggplot(mpg, aes(class, fill = 1)) +
  geom_bar(colour = "black") +
  scale_fill_y_viridis_c()
```

Discretise gradients with binned scales:

```{r}
ggplot(mpg, aes(hwy, fill = 1)) +
  geom_density() +
  scale_fill_x_binned()
```

Flexibly specify gradients with the syntax of regular fill scales:

```{r}
ggplot(mpg, aes(hwy, class, fill = 1)) +
    geom_boxplot() +
    scale_fill_x_distiller(
        name = "hwy",
        limits = c(25, 30),
        oob = scales::oob_squish,
        palette = "RdBu",
        direction = 1,
        group = FALSE
    )
```
